An iterated Grothendieck construction of semi-cubical types

### 2021-07-17 paper/paper.tex
[Cubical] Replace epsilon' with omega
[paper] Start writing Grothendieck construction

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, tikz-cd, booktabs, setspace, makecell, caption, floatrow, amsthm, lmodern}
\usepackage[margin=0.3in]{geometry}

@@

\title{An indexed construction of semi-cubical types}
\author{Ramkumar Ramachandra}
\author{Hugo Herbelin}

@@

  $$
    \begin{tikzcd}
      1 \arrow[r, dash] & 1' \arrow[d, dash] \\
      0 \arrow[u, dash] & 0' \arrow[l, dash]
    \end{tikzcd}
  $$
\end{example}

@@

Then, the first viewpoint corresponding to the one in simplicial sets is uninteresting for our purposes. Let us, instead, elaborate on the second viewpoint:

@@

  \begin{align*}
    X_n       & := X(\I{n}) = \text{Hom}(\I{n}, X), \text{where X is the semi-cubical set} \\
    X_\lambda & := X(\lambda)
  \end{align*}
\end{definition}

@@

@@

\begin{eqntable}{\label{tab:barecubicalsetstructurecore} Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
  \mc{Type of truncated cubical sets} \\
  \eqnline{\partialcubset{l}{n}}{}{:}{\sort{l+1}}
  \eqnline{\partialcubset{l}{0}}{}{\defeq}{\unittype}
  \eqnline{\partialcubset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)}

@@

\begin{thebibliography}{10}
  \bibitem{Bezem14}
  Bezem, M., Coquand, T., \& Huber, S. (2014, July). A model of type theory in cubical sets. \textit{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol. 26, pp. 107-128). Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.

  \bibitem{Friedman08}
  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \textit{arXiv preprint arXiv:0809.4221}.

  \bibitem{Riehl11}
  Riehl, E. (2011). A leisurely introduction to simplicial sets. \textit{Unpublished expository article available online at \href{http://www.math.harvard.edu/~eriehl}{http://www.math.harvard.edu/~eriehl}}.

  \bibitem{Antolini00}
  Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.

  \bibitem{Herbelin15}
  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
\end{thebibliography}

>>>>

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, tikz-cd, booktabs, setspace, makecell, caption, floatrow, amsthm, mathrsfs, lmodern}
\usepackage[margin=0.3in]{geometry}

@@

% Type theory
\newcommand{\U}{\ensuremath{\mathscr{U}}}

\title{An iterated Grothendieck construction of semi-cubical types}
\author{Ramkumar Ramachandra}
\author{Hugo Herbelin}

@@

  $$
    \begin{tikzcd}
      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
    \end{tikzcd}
  $$
\end{example}

@@

Or, in terms of objects and morphisms:

@@

  \begin{align*}
    X_n       & := X(\I{n}), \text{where X is the semi-cubical set} \\
    X_\lambda & := X(\lambda)
  \end{align*}
\end{definition}

@@

\section{Iterated Grothendieck construction}

The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.

$$
  \begin{tikzcd}
    X_0 : \U & X_1 : \U \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
$$

\begin{align*}
  X_0 & : \U                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \U                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U \\
  \ldots
\end{align*}

@@

\begin{eqntable}{\label{tab:barecubicalsetstructurecore} Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
  \mc{Type of truncated cubical sets}
  \eqnline{\partialcubset{l}{n}}{}{:}{\sort{l+1}}
  \eqnline{\partialcubset{l}{0}}{}{\defeq}{\unittype}
  \eqnline{\partialcubset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)}

@@

\begin{thebibliography}{10}
  \bibitem[Bez]{Bezem14}
  Bezem, M., Coquand, T., \& Huber, S. (2014, July). A model of type theory in cubical sets. \textit{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol. 26, pp. 107-128). Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.

  \bibitem[Fri]{Friedman08}
  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \textit{arXiv preprint arXiv:0809.4221}.

  \bibitem[Rie]{Riehl11}
  Riehl, E. (2011). A leisurely introduction to simplicial sets. \textit{Unpublished expository article available online at \href{http://www.math.harvard.edu/~eriehl}{http://www.math.harvard.edu/~eriehl}}.

  \bibitem[Ant]{Antolini00}
  Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.

  \bibitem[Her]{Herbelin15}
  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
\end{thebibliography}
